\documentclass[12pt,letterpaper,sans]{moderncv}

\moderncvtheme[blue]{classic}

\usepackage[utf8]{inputenc}
\usepackage[scale=0.88]{geometry}
\usepackage{color}
\usepackage{enumitem}
\setlist{nosep}

\definecolor{lightgrey}{rgb}{0.6,0.6,0.6}
\definecolor{darkgrey}{rgb}{0.4,0.4,0.4}
\firstname{\textcolor{lightgrey}{Matt}}
\familyname{\textcolor{darkgrey}{Hoffman}}
\title{Software Engineer}
\address{304 N Wallace Blvd}{Ypsilanti, MI 48197}
\mobile{734-353-0820}
\email{hofmadresu@gmail.com}
\homepage{about.me/hofmadresu}
\recomputelengths

\begin{document}

\maketitle
\vspace*{-5mm}

\section{Programming Languages}
\subsection{Proficient With:}
\cvline{}{C\#, JavaScript, HTML, CSS, LESS, SQL}
\subsection{Experience With:}
\cvline{}{Clojure, Java, Scala, VB.NET, Cold Fusion}
\section{Technologies and Tools}
\subsection{Proficient With:}
\cvline{}{.NET Stack (ASP.NET MVC, Web API, Entity Framework), Xamarin, Android, iOS, SQL Server, DurandalJS, \mbox{KnockoutJS}, jQuery, BreezeJS, RabbitMQ, Quartz.NET, Visual Studio, \mbox{SQL Server Management Studio}, Vim, Git, Telerik's JustTrace}
\subsection{Experience With:}
\cvline{}{Power Pivot, Eclipse, Chrome Developer Tools, Bootstrap, Subversion, Lieningen, JetBrain's DotTrace, Redis, Azure}

\section{Experience}
\cventry{2014--Present}{Co-Founder}{\href{http://fudi.st}{Fudist}}{}{}{}
    \begin{itemize}[leftmargin=1.24in]
    	\item Primary developer of Android and iOS mobile clients
		\item Designed and developed major new feature to recommend meals to users
		\item Developed and enhanced server-side C\# code
    	\item Improved performance of back end code and database
    	\item Evaluated technologies to use in both the mobile and server applications
    	\item Interviewed customers to determine what enhancements were needed
    	\item Designed UI for new screens for both the mobile application and the Fudist website
    	\item Integrated with Apple, Google, and Stripe to create a subscription system	
    \end{itemize}
\cventry{2008--2014}{Senior Consultant}{\href{http://www.xby2.com}{X by 2, Inc.}}{Farmington Hills, MI}{}{}
    \begin{itemize}[leftmargin=1.24in]
        \item Financial Management System Upgrade (Team Lead / Architect)
            \begin{itemize}
                \item Played key leadership role in replacing a financial services company's primary internal software with a custom application built on a Durandal front end and .NET back end.
                \item Worked with other architects and team leads to design and implement a module-by-module replacement of the old system.
                \item Created prototypes and initial versions of major architectural components, including message queue \mbox{communication} between different applications and integration of the new and old systems.
                \item Profiled and improved memory usage and speed of key application components.
                \item Mentored and reviewed code for junior developers.
            \end{itemize}
                                \newpage
        \item Health Insurance Data Warehouse (Developer)
        	\begin{itemize}
	        	\item Worked on several data import, export and reporting integrations.
	        	\item Performance tuned long-running SQL queries.
	        	\item Helped create a system to automate database and ETL deployment to testing and production servers using Red Gate APIs and custom C\# code.
	        	\item Mentored junior developers and interns.
        	\end{itemize}
        \item Electronic Medical Record System (Developer)
            \begin{itemize}
                \item Worked with a team to develop the data model and web services for a care delivery platform that provides physicians with a single source for patient health information management.
                \item Used Visual Studio and SQL Server Management Studio tools to identify and correct performance and scalability bottlenecks.
            \end{itemize}
        \item Website improvement and maintenance (Developer / Client Contact)
        	\begin{itemize}
        		\item Maintained and improved web applications for several clients in various technologies.
        		\item Operated as primary contact for clients. This involved fielding calls, fixing and improving applications and managing junior employees.
        	\end{itemize}
        \item Internal Roles at X by 2 (Developer / Administrator)
            \begin{itemize}
            	\item Initiated and led monthly event for developers to explore new technologies without pressure from deadlines or client expectations.
                \item Developed and maintained a new vacation, travel and incentive tracking application.
                \item Helped develop a new time tracking system to replace an older application that was difficult to maintain.
                \item Created an employee utilization report which replaced a weekly report that was generated manually in Excel.
                \item Created an application using SignalR and Redis which allowed employees to suggest and vote on places to go for lunch.
                \item Set up, administered and maintained internal SharePoint website.
            \end{itemize}
    \end{itemize}


\section{Education}
\cventry{2004--2008}{BS, Computer Science Engineering}{University of Michigan}{}{}{}

\section{Activities}
\cventry{2014--Present}{Ann Arbor .NET Developers}{.NET User Group}{}{}{}
\cventry{2014--Present}{Craftsman Guild}{Technology Agnostic User Group}{}{}{}
\cventry{2013--Present}{MiGang}{Great Lakes Area .NET User Group}{}{}{}
\cventry{2013--Present}{SEM-JS}{JavaScript User Group}{}{}{}
\cventry{2005--2008}{Michigan Marching Band}{}{}{}{}
\cventry{1997--2004}{Boy Scouts of America}{}{}{}{Eagle Scout}

\end{document}
